{\includegraphics[width=3cm, height=2.5cm]{Cran.jpg}} \\ \includegraphics[width=7cm, height=1cm]{TB.jpg} \\ {Technical Documentation for TersectBrowser+}

### 2025-05-05 TechDoc/TechDoc.tex
add search extension docs

\subsubsection{Future Improvements}
The gene models track could be expanded to display alternative splicing events, offering a clearer view of transcript diversity. Additionally, adding a hover-based popup over each bin that displays gene models for accessions containing variants could offer a rapid and informative view of variant differences.

@@

\subsubsection{User Interface}
\begin{figure}[h]
    \centering
    \includegraphics[width=15cm, height=9cm]{FS1.png}
    \caption{UI digram for Feature Search.}
\end{figure}

\paragraph{Feature Description}
\begin{itemize}
    \item \verb+Open Variant Search+ button in TersectBrowser+ header, opens popup window for user to select advanced features.
    \item Popup window where user can select interval, choose impact level, and search button to initiate search.
    \item Output: Bins in the canvas are highlighted red at the chromosomal position where the variant is located, and only for accessions containing variants of the specified impact.
    \item Clear button located in TersectBrowser+ header to clear highlighted bins from canvas and restore original heatmmap.
\end{itemize}
\subsection*{4.3.3 Feature Search Extension – Technical Description}

@@

\section {References}
\begin{thebibliography}{9}
\bibitem{ucsc_trix}
University of California, Santa Cruz. (n.d.). Trix Index Files. UCSC Genome Browser.
\end{thebibliography}
\end{document}

>>>>

@@

\subsubsection{User Interface}
\paragraph{Feature Description}
\begin{itemize}
    \item \verb+Open Variant Search+ button in TersectBrowser+ header, opens popup window for user to select advanced features.
    \item Popup window where user can select interval, choose impact level, and search button to initiate search.
    \item Output: Bins in the canvas are highlighted red at the chromosomal position where the variant is located, and only for accessions containing variants of the specified impact.
    \item Clear button located in TersectBrowser+ header to clear highlighted bins from canvas and restore original heatmmap.
\end{itemize}

\subsection*{4.3.3 Feature Search Extension – Technical Description}

@@

\section {References}

\end{document}
